The evolution of gene expression in the term placenta of viviparous mammals

### 2015-11-21 manuscript/manuscript.Rnw
add discussion of tissue specificity index

To evaluate the extent of tissue specificity of each gene, we
calculated the tissue specificity index based on human microarray data
from (Su et al., 2004) available via BioGPS. The tissue specificity
index (TSI) measures the extent to which a specific gene has
predominant expression in only one tissue (Yanai et al., 2005). A TSI
of 1.0 would signify that a gene was solely expressed in only one
tissue, while a TSI of 0.0 would signify that a gene had equal
expression in all tissues evaluated. We used the formula available in
Yanai et al. (2005) to calculate the TSI, and identified the top four
tissues which expressed each probe set from (Su et al., 2004).

>>>>

To evaluate the extent of tissue specificity of each gene, we
calculated the \ac{TSI} based on human RNASeq data in 3267 samples in
126 tissues the Roadmap Epigenomics
\cite{Bernstein.ea2010:NIHRoadmapEpigenomicsMapping} and GTEx projects
\cite{Gtexconsortium.2015:Thegenotypetissueexpression} as well
additional placenta
\cite{Hughes.ea2015:Evaluatingintra-andinter-individual} and uterus
\cite{Chan.ea2014:Assessmentofmyometrialtranscriptome} samples from
SRA. The \ac{TSI} measures the extent to which a specific gene has
predominant expression in only one tissue
\cite{Yanai.ea2005:Genome-widemidrangetranscriptionprofiles}. A gene
expressed in only one tissue would have a \ac{TSI} of 1, whereas a
gene expressed in all tissues would have a \ac{TSI} of 0.
